Making Sequential Programs Deterministic

### 2019-04-03 randoop-case-study.tex
Add another bug found, and a description of the process

\item  \textbf{Bug 3:}
Diagnostic output that printed a hash code for brevity, but should have had deterministic output\commit{661a4970}.  By contrast to the other two bugs, this one is not serious.
\end{itemize}

We reported another suspicious case of order-nondeterminism, in the
\<findOverridden> method.  The Randoop developers explained it was
acceptable, after tracing the flow through the program.  (One said, ``This
looks OK to me \ldots\ it took me a little while to decide that.'')  The fact
depended on subtle, undocumented invariants about Randoop that we had not
been able to reverse-engineer.

>>>>

\item \textbf{Bug 3:}
Diagnostic output that printed a hash code for brevity, but should have had
deterministic output\commit{661a4970}.  By contrast to the first two bugs,
this one is not serious.

\item \textbf{Bug 4:}
Diagnostic output that printed a timestamp, but should have obeyed an
option about whether to do so\commit{a460df97}.  By contrast to the first
two bugs, this one is not serious.

\end{itemize}

We reported another suspicious case of order-nondeterminism, in the
\<SpecificationCollection>\-\<.findOverridden> method.  The Randoop developers explained it was
acceptable, after tracing the flow through the program.  (One said, ``This
looks OK to me \ldots\ it took me a little while to decide that.'')  The fact
depended on subtle, undocumented invariants about Randoop that we had not
been able to reverse-engineer.

We annotated one package at a time, starting with the most central packges
that are most depended upon.  Within a package, we followed a similar
strategy, annotating supertypes first.  If the classes and methods had been
documented with respect to their determinism, then our annotation effort
would have been easy, just converting English into type qualifiers.
Unfortunately, this was not the case: we reverse-engineered each
specification, largely from the methods it calls.  Sometimes after we
annotated a subclass, we had to go back and change existing annotation on
the supertype or elsewhere.
After resolving most type-checking warnings by adding or changing
annotations, we manually examined each remaining one to determine whether
it was a bug or a false positive warning.
